How to use flowCore package

### 2007-02-05 inst/doc/HowTo-flowCore.Rnw
Fix vignette
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@22337 bc3139a8-67e5-0310-9ffc-ced21a209358
vignette andd man pages fixes
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@22434 bc3139a8-67e5-0310-9ffc-ced21a209358

\bibliographystyle{plainnat}

@@

We can plot the raw data for the FSC-H and SSC-H parameters.
<<plotRaw1,eval=TRUE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(1,2))
@
<<plotRaw2,eval=TRUE,echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(3,4))
@ 
\begin{verbatim}
> plot(b08,plotParameters=c(1,2))
> plot(b08,plotParameters=c(3,4))
> plot(e07,plotParameters=c(1,2))
> plot(f06,plotParameters=c(1,2))
\end{verbatim}

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotRaw1} A}
\subfigure{\includegraphics[width=40mm]{plotRaw2} B}
\caption{
  \label{fig:Fig01}{Example of smooth scatter plot.(A) FSC-H
    \textit{vs.} SSC-H (B) FL2-H \textit{vs.} FL3-H}} 
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotTofilter} A}
\subfigure{\includegraphics[width=40mm]{plotfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plot3} A}
\subfigure{\includegraphics[width=40mm]{plot4} B} 
\caption{
  \label{fig:Fig03}{Second example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

%%\begin{figure}
%%\\centering
%%\\subfigure{\includegraphics[width=40mm]{plotRectanglefilter} A}
%%\\subfigure{\includegraphics[width=40mm]{plotTrianglefilter} B} 
%%\\caption{
%%\  \label{fig:Fig03}{Example of the effect of filtering with a
%%\    polygon gate.}} 
%%\\end{figure}

@@

<<rawdata1, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,plotParameters=c("FSC-H","SSC-H"),main="B08")
@
<<rawdata2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>= 
plot(e07,plotParameters=c("FSC-H","SSC-H"),main="E07")
@
<<rawdata3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,plotParameters=c("FSC-H","SSC-H"),main="F06")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{rawdata1}}
%%\subfigure{\includegraphics[width=40mm]{rawdata2}} 
%%\subfigure{\includegraphics[width=40mm]{rawdata3}} 
%%\caption{
%%  \label{fig:Fig04}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<SelectNonDebris,eval=TRUE,echo=FALSE,results=hide>>=
filter1 <- rectangleGate(filterId="nonDebris","FSC-H"=c(0.2,0.8),"SSC-H"=c(0,0.8))
b08.result1 <-  filter(b08,filter1)
##e07.result1 <- filter(e07,filter1)
##f06.result1 <- filter(f06,filter1)
summary(b08.result1)
##tab <- c("B08"=sum(b08.result1@subSet),"E07"=sum(e07.result1@subSet),"F06"=sum(f06.result1@subSet))
@ 
<<plotResFilter1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result1,main="B08 nonDebris",pch="*")
@ 
<<plotResFilter2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(e07,y=e07.result1,main="E07 nonDebris",pch="*")
@ 
<<plotResFilter3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,y=f06.result1,main="F06 nonDebris",pch="*")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{plotResFilter1}}
%%\subfigure{\includegraphics[width=40mm]{plotResFilter2}} 
%%\subfigure{\includegraphics[width=40mm]{plotResFilter3}} 
%%\caption{
%%  \label{fig:Fig05}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<plotLivingCell1, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result2,parent=b08.result1,xlim=c(0,1024),ylim=c(0,1024),main="B08",pch="*")
@ 
<<plotLivingCell2, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(e07,y=e07.result2,parent=e07.result1,xlim=c(0,1024),ylim=c(0,1024),main="E07",pch="*")
@ 
<<plotLivingCell3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,y=f06.result2,parent=f06.result1, xlim=c(0,1024),ylim=c(0,1024),main="F06",pch="*")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{plotLivingCell1}}
%%\subfigure{\includegraphics[width=40mm]{plotLivingCell2}} 
%%\subfigure{\includegraphics[width=40mm]{plotLivingCell3}} 
%%\caption{
%%  \label{fig:Fig06}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

\clearpage
\bibliographystyle{cyto} 
\bibliography{cytoref}
\clearpage
\small{
<<sessionInfo>>=
sessionInfo()
@ 
}
\end{document}

>>>>

@@

We can plot the raw data for the FSC-H and SSC-H parameters.
<<plotRaw1,eval=TRUE, echo=FALSE,fig=TRUE, prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(1,2))
@
<<plotRaw2,eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(3,4))
@ 
\begin{verbatim}
> plot(b08,plotParameters=c(1,2))
> plot(b08,plotParameters=c(3,4))
> plot(e07,plotParameters=c(1,2))
> plot(f06,plotParameters=c(1,2))
\end{verbatim}

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.4\textwidth]{plotRaw1} A}
\subfigure{\includegraphics[width=0.4\textwidth]{plotRaw2} B}
\caption{
  \label{fig:Fig01}{Example of smooth scatter plot.(A) FSC-H
    \textit{vs.} SSC-H (B) FL2-H \textit{vs.} FL3-H}} 
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.4\textwidth]{plotTofilter} A}
\subfigure{\includegraphics[width=0.4\textwidth]{plotfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.4\textwidth]{plot3} A}
\subfigure{\includegraphics[width=0.4\textwidth]{plot4} B} 
\caption{
  \label{fig:Fig03}{Second example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotRectanglefilter} A}
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotTrianglefilter} B} 
%%\caption{
%%  \label{fig:Fig03}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<rawdata1, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,plotParameters=c("FSC-H","SSC-H"),main="B08")
@
<<rawdata2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>= 
plot(e07,plotParameters=c("FSC-H","SSC-H"),main="E07")
@
<<rawdata3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,plotParameters=c("FSC-H","SSC-H"),main="F06")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=0.4\textwidth]{rawdata1}}
%%\subfigure{\includegraphics[width=0.4\textwidth]{rawdata2}} 
%%\subfigure{\includegraphics[width=0.4\textwidth]{rawdata3}} 
%%\caption{
%%  \label{fig:Fig04}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<SelectNonDebris,eval=TRUE,echo=FALSE,results=hide>>=
filter1 <- rectangleGate(filterId="nonDebris","FSC-H"=c(0.2,0.8),"SSC-H"=c(0,0.8))
b08.result1 <-  filter(b08,filter1)
##e07.result1 <- filter(e07,filter1)
##f06.result1 <- filter(f06,filter1)
summary(b08.result1)
##tab <- c("B08"=sum(b08.result1@subSet),"E07"=sum(e07.result1@subSet),"F06"=sum(f06.result1@subSet))
@ 
<<plotResFilter1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result1,main="B08 nonDebris",pch="*")
@ 
<<plotResFilter2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(e07,y=e07.result1,main="E07 nonDebris",pch="*")
@ 
<<plotResFilter3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,y=f06.result1,main="F06 nonDebris",pch="*")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotResFilter1}}
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotResFilter2}} 
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotResFilter3}} 
%%\caption{
%%  \label{fig:Fig05}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<plotLivingCell1, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result2,parent=b08.result1,xlim=c(0,1024),ylim=c(0,1024),main="B08",pch="*")
@ 
<<plotLivingCell2, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(e07,y=e07.result2,parent=e07.result1,xlim=c(0,1024),ylim=c(0,1024),main="E07",pch="*")
@ 
<<plotLivingCell3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,y=f06.result2,parent=f06.result1, xlim=c(0,1024),ylim=c(0,1024),main="F06",pch="*")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotLivingCell1}}
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotLivingCell2}} 
%%\subfigure{\includegraphics[width=0.4\textwidth]{plotLivingCell3}} 
%%\caption{
%%  \label{fig:Fig06}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

\clearpage
\bibliographystyle{plainnat} 
\bibliography{cytoref}
\clearpage
\small{
<<sessionInfo>>=
sessionInfo()
@ 
}
\end{document}
